---
title: "our week 2"
author: "Jialuo Li"
date: "9/19/2021"
output:
  pdf_document: default
  github_document:
    df_print: paged
  html_document:
    df_print: paged
---
## Git hub link:
https://github.com/JialuoLi/New-repo

it's at the bottom of the file list

## (1)
```{r include=FALSE}

library(dplyr)

# install.packages("nycflights13")
library(nycflights13)
library(ggplot2)
library(tibble)
```

```{r}
filter(flights,is.na(dep_time))
```
8255 flights have missing dep_time. seems that dep_delay, arr_time and arr_delay also have the same missing value. They may mean the delay of departure, arrive of time and delay of arrival. Bacause they are canceled thus no such values.

## (2)
```{r}
transmute(flights,deptime=60*dep_time %/% 100+dep_time %% 100, scedtime=60*sched_dep_time %/% 100+sched_dep_time %% 100)
  
```
since the thousand and hundred digit are hours, ten and unit are minute, we just need to multiply hours by 60 and add it by minute.

## (3)
```{r}
Delay<-flights %>% group_by(year,month,day) %>% summarise(Mean = mean(arr_delay,na.rm = TRUE),cancel=sum(is.na(arr_delay)|is.na(dep_delay)), canceled_rate=sum(is.na(arr_delay))/n())



head(Delay)

ggplot(data = Delay, mapping = aes(x=Mean, y=canceled_rate)) +
  geom_point()
```






Seems that the canceled rate increases when the mean of delay time increases

